---
title: "Week 2"
author: "tp"
date: "2023-07-19"
output: html_document
---

*This text will appear in italics!*
**This text will appear in bold!**

# Primary Heading
## Secondary Heading
### Tertiary Heading

# Unordered Lists
- First item
- Second item
- Third item


* Can also use asterisk
* as in this list

# Ordered Lists

1. Or a numbered list
2. Like so
6. And the numbering
3. Doesn't need to be in order

# Links

[Johns Hopkins](https://publichealth.jhu.edu/)

[RStudio](https://posit.co/)

Here I can add links to [R bloggers][1] and [Simply Statistics][2]!

[1]:https://www.r-bloggers.com/ "R bloggers"
[2]:https://simplystatistics.org/ "Simply Statistics"

New lines Require a double space after the end of a line  
Like so


Here is a code chunk where the code will be hidden, only result will show
```{r simulation, echo = FALSE}
set.seed(1)
x <- rnorm(100)
mean(x)
```

Here i will name the code chunk and create vars to populate within a sentence
```{r computetime, echo=F}
time <- format(Sys.time(), "%a %b %d %X %Y")
rand <- rnorm(1)
```

The current time is `r time`. My favorite random number is `r rand`.


## Now lets incorporate some graphics. First we will sim some data
```{r simdata, echo=T}
x <- rnorm(100); y <- x + rnorm(100, sd = 0.5)
```

## Here is a scatter plot of the data
```{r scatterplot, fig.height=4}
par(mar = c(5,4,1,1), las=1)
plot(x,y, main = "My Sim Data")
```


## Making Tables

```{r fitmodel}
fit <- lm(Ozone ~ Wind + Solar.R + Temp, data = airquality)
```

```{r showtable, results="asis"}
library(xtable)
xt <- xtable(summary(fit))
print(xt, type = "html")
```


## Setting global options

```{r setoptions, echo=F}
library(knitr)
opts_chunk$set(echo = FALSE, results = "hide")
```

## cache = TRUE
After first run, results are loaded from cache, use cache=TRUE  
This is helpful for code chunks that take a long time to run  






